---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

## A Comparative Analysis of Wi-Fi Performance Between Science and Humanities Buildings: Evidence of Infrastructure Inequality on a College Campus

```{r}
# if not installed use: install.packages("package_name")
library(readxl)
library(psych)

hanson_data= read_excel("datasheet.xlsx", sheet="Hanson")
oldmain_data= read_excel("datasheet.xlsx", sheet="Old Main")
```

$H_T$: There is no difference in average wifi speed between Old Main and Hanson

$H_A$: There is a difference in average wifi speed between Old Main and Hanson

$\alpha=0.05$

### Abstract

Lorem

## I. Introduction

Lorem

## II. Experimental Setup

```{r}
# get the differece between download and upload speeds for each building
result <- data.frame(download_diff = hanson_data$`Download Speed (Mbps)` - oldmain_data$`Download Speed (Mbps)`, 
                     upload_diff = hanson_data$`Upload Speed (Mbps)` - oldmain_data$`Upload Speed (Mbps)`)

```

Here is a summary of the data:

```{r}
summary(result$download_diff)
```

```{r}
summary(result$upload_diff)
```

Now to get some of the statistics:

```{r}
download_sd <- sd(result$download_diff)
download_mean <- mean(result$download_diff)

upload_sd <- sd(result$upload_diff)
upload_mean <- mean(result$upload_diff)

#use ggplot2
library(ggplot2)

plot_dist_hist <- function(n,mean,sd,binwidth) {
  df <- data.frame(x = rnorm(n, mean, sd))
  ggplot(df, aes(x = x, mean = mean, sd = sd, binwidth = binwidth, n = n)) +
    theme_bw() +
    geom_histogram(binwidth = binwidth, 
        colour = "white", fill = "cornflowerblue", linewidth = 0.1) +
stat_function(fun = function(x) dnorm(x, mean = mean, sd = sd) * n * binwidth,
    color = "darkred", linewidth = 1)
}
n = 16
binwidth = 50 # passed to geom_histogram and stat_function
set.seed(1)


plot_dist_hist(n, download_mean, download_sd, binwidth) + labs( title = "Plot of Average Download Speed Difference Distribution", x="Speed (Mbps)", y="Occurance")
plot_dist_hist(n, upload_mean, upload_sd, binwidth)+ labs( title = "Plot of Average Upload Speed Difference Distribution", x="Speed (Mbps)", y="Occurance")

```

## III. Results

Lorem

## IV. Discussion

Lorem

## References

Using IEEE Style
