---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

## A Comparative Analysis of Wi-Fi Performance Between Science and Humanities Buildings: Evidence of Infrastructure Inequality on a College Campus

```{r}
# if not installed use: install.packages("package_name")
library(readxl)
library(psych)

hanson_data= read_excel("datasheet.xlsx", sheet="Hanson")
oldmain_data= read_excel("datasheet.xlsx", sheet="Old Main")

oldmain_data
```

$H_T$: There is no difference in average wifi speed between Old Main and Hanson

$H_A$: There is a difference in average wifi speed between Old Main and Hanson

### Abstract

Lorem

## I. Introduction

Lorem

## II. Experimental Setup

```{r}
# get the differece between download and upload speeds for each building
result <- data.frame(download_diff = hanson_data$`Download Speed (Mbps)` - oldmain_data$`Download Speed (Mbps)`, 
                     upload_diff = hanson_data$`Upload Speed (Mbps)` - oldmain_data$`Upload Speed (Mbps)`)

head(result)
```

Here is a summary of the data:

```{r}
summary(result$download_diff)
```

```{r}
summary(result$upload_diff)
```

Now to get some of the statistics:

```{r}
download_sd <- sd(result$download_diff)
download_mean <- sd(result$download_diff)

upload_sd <- sd(result$upload_diff)
upload_mean <- sd(result$upload_diff)
```

## III. Results

Lorem

## IV. Discussion

Lorem

## References

Using IEEE Style
